Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
shannon

Sparse Distributed Memory (SDM) \citep{Kanerva1988} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from clues of the present. For instance, when one is walking on a dark alley and is afraid of something, one cannot explain where one's fear come from. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. This flexibility into mapping one situation in another is an important human feature which is hard to replicate in computers.

@@

\begin{figure}[h!]
  \centering
  \subfloat[$w_2(d), d \in \{ 1, 2, ..., n\}.$]{\includegraphics[width=3.2in]{./images02/info-theory/weights.png}}

  \subfloat[$w_2(d)$ for the desired range.]{\includegraphics[width=3.2in]{./images02/info-theory/weights-region.png}}

  \subfloat[Stepwise $\left \lfloor{w_1(d)}\right \rfloor$ for fast integer computation.]{\includegraphics[width=3.2in]{./images02/info-theory/weights-region-stepwise.png}}

@@

The initial results of this \emph{Shannon write} operation can be seen in Figure \ref{fig:info-theory-experiments} and seem promising. It seems that, when $n=1,000$, $H=1,000,000$, $r=451$, and 10,000 written random bitstrings, the critical distance increased from around 221 to around 250. This increase may be interpreted as an improvement in SDM, because it would converge to the correct bitstring even for farther bitstrings. Note that 29 additional bits imply an attractor area $2^{29}$ times larges than the original. It may affect memory capacity, possibly increasing it.

Another point to keep in mind is that, since the modulus of the vectors are not uniform in this approach, that the shape of the attractor may have asymmetries.

>>>>

Sparse Distributed Memory (SDM) \citep{Kanerva1988} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from clues of the present. For instance, when one is walking on a dark alley and is afraid of something, one cannot explain where one's fear come from. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing precisely what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. This flexibility into mapping one situation in another is an important human feature which is hard to replicate in computers.

@@

\begin{figure}[h!]
  \centering
  \subfloat[$w(d), d \in \{ 1, 2, ..., n\}.$]{\includegraphics[width=3.2in]{./images02/info-theory/weights.png}}

  \subfloat[$w(d)$ for the desired range.]{\includegraphics[width=3.2in]{./images02/info-theory/weights-region.png}}

  \subfloat[Stepwise $\left \lfloor{w(d)}\right \rfloor$ for fast integer computation.]{\includegraphics[width=3.2in]{./images02/info-theory/weights-region-stepwise.png}}

@@

The initial results of this \emph{Shannon write} operation can be seen in Figure \ref{fig:info-theory-experiments} and seem promising. It seems that, when $n=1,000$, $H=1,000,000$, $r=451$, and 10,000 written random bitstrings, the critical distance increased from around 221 to around 250. This increase may be interpreted as an improvement in SDM, because it would converge to the correct bitstring even for farther bitstrings. Note that 29 additional bits imply an attractor area $2^{29}$ times larger than the original. This Shannon write may affect memory capacity --- possibly increasing it. Another point to keep in mind is that, since the modulus of the vectors are not uniform in this approach, that the shape of the attractor may have asymmetries. Whereas these are just some initial tests, the idea seems meritorious so far.  As for future research, we will execute all tests in the thesis and compare this Shannon write with the original Kanerva model.
